m0.0.1: Microxanox - ...

### 2022-03-15 inst/manuscript/manuscript_microxanox.Rmd
Update manuscript_microxanox.Rmd
Dear Rainer, I made some suggestions. Please take a look and we should then briefly discuss. Cheers, Owen

## The ODEs
The ODEs for the rates of change are specified in the function `bushplus_dynamic_model()`. This augmented version of the model published in [@Bush2017] can handle multiple strains within each of the three functional groups, temporal variation in oxygen diffusivity, and events.

For an example how these can be used see [@REF_NEEDED] or the vignettes acompanying this package [@LINK_NEEDED].

@@

# The Package
The package contains the full documentetion of the functions, which includes

@@

@@

The simulations can be split into different levels:

## The individuel simulation
The individual simulation (`run_simulation()` function) is the working horse in this package. In this function, the ODEs are solved. The function needs only one parameter - an object as created by the function `new_runsim_parameter()`. One parameter of this object is the `strain_parameter` which can be created by the function `new_strain_parameter()`. For a detailed description of the parameter and how they are created please see the User Guide and which acomnpanies the package or is available at [User Guide](@LINK_NEEDED)

@@

## Find a Steady State of the model
There are two methods for finding steady states. The first runs a separate simulation for each combination of starting conditions and oxygen diffusivity (let us term this the *Replication method*). The second runs only two simulations, with step-wise and slowly temporally increasing or decreasing oxygen diffusivities and recorded of state just before change to a new oxygen diffusivity (let us term this the *Temporal method*).

@@

## Analysis and Graphing

@@

@@

# Use cases
This package has been used in the production of the paper [@REF_NEEDED]. It can be used for similar studies in this study systems. It is not intended to provide a modelling framework which can be adjusted easily to all needs, but primarily a tool to implement the model used by [@Bush2017] and to extend it to our needs. Consequently, any more substantial, are likely to need a change in the source code.

>>>>

@@

# Using the package

## Documentation

The package contains the full documentetion of the functions, which includes

@@

## The simulation framework

Here make an overview of how conditions and parameters are specified, stored, and results stored. I think there is text in the user guide vignette that can be used (duplicated) here.

@@

The ODEs for the rates of change are specified in the function `bushplus_dynamic_model()`. This augmented version of the model published in [@Bush2017] can handle multiple strains within each of the three functional groups, temporal variation in oxygen diffusivity, and events.

In the following sections we describe the general goals of the package: running one simulation, finding steady states across an environmental gradient, calculating measures of stability, and visualisation.

## Running one simulation

The individual simulation (`run_simulation()` function) is the working horse in this package. In this function, the ODEs are solved. The function needs only one parameter - an object as created by the function `new_runsim_parameter()`. One parameter of this object is the `strain_parameter` which can be created by the function `new_strain_parameter()`. For a detailed description of the parameter and how they are created please see the User Guide and which acomnpanies the package or is available at [User Guide](@LINK_NEEDED)

@@

## Find a Steady State of the model

There are two methods for finding steady states. The first runs a separate simulation for each combination of starting conditions and oxygen diffusivity (let us term this the *Replication method*). The second runs only two simulations, with step-wise and slowly temporally increasing or decreasing oxygen diffusivities and recorded of state just before change to a new oxygen diffusivity (let us term this the *Temporal method*).

@@

## Visualisation

@@

**Please include figures so they can have captions and be cross referenced, as in the Supplement.**

@@

# Use cases

The first two use cases come from the User Guide and the Partial Reproduction Vignettes. The third comes from a research article that relied on the package.

## Regime shifts during temporal environmental change

Take from the user guide.

## The extent of hysteresis depends on community composition

Take from the partial reproduction.

## Effects of functional diversity on regime shifts

This package has been used in the production of the paper [@REF_NEEDED]. It can be used for similar studies in this study systems. It is not intended to provide a modelling framework which can be adjusted easily to all needs, but primarily a tool to implement the model used by [@Bush2017] and to extend it to our needs. Consequently, any more substantial, are likely to need a change in the source code.
